The Exoplanet Orbit Database \textsc{II}: Updates to exoplanets.org

### 2014-07-22 draft/ms.tex
Remove upper limit from sec:unc and incorporate Ming's comments.

Also for plotting convenience, for transiting $Kepler$ planets without $m\sin{i}$ measured, we estimate their mass using 
mass-radius relations from the literature. We follow a series of
relations given by \footnote{As of the writing of this manuscript,
  Kepler planet candidates on exoplanets.org ingested
  from the Exoplanet Archive have their masses estimated in a slightly
  different manner.  The Website uses the \citeauthor{Mordasini2012} relation for
  planets with 6$\rearth < R < 1 $ \rjup, the \citeauthor{Lissauer2011}
  relation between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in
  Earth units for planets smaller than $\rearth$.  Updating this
  relation to be consistent with the EOD (and updating the
  corresponding MASSREF fields for these candidates) is a priority
  upgrade for exoplanets.org.}

@@

%------------------------------------------------------------------------------
\subsection{Uncertainties and Upper Limits}\label{sec:unc}

@@

If only an upper limit is given, we set the parameter field X to 0,
and store the upper limit value in the field XUL. The uncertainty UX
is set to half of the upper limit, and the upper error bar XUPPER to
the upper limit value. For example, if the literature reports the
upper limit for ECC, which we report in ECCUL, then we set ECC to be
0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We are currently
implementing a more precise upper limit scheme (see
Section~\ref{sec:summary}.)

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/senew.eps}
\caption{An example plot that demonstrates the current secondary
  eclipse measurements. Each planet has a set of circles that stand
  for its available secondary eclipse measurements in the database,
  including \spitzer\ 8.0, 5.8, 4.5, \& 3.6 \micron, and ground-based
  $J$, $H$, and $K_{\rm s}$ bands. \kepler\ secondary eclipse measurements
  are labeled as solid black dots. A few representative planets are
  also annotated (a feature not offered by the EDE Plotter, but
  trivially implemented by other image or presentation software).}
\label{fig:se}
\end{figure}

@@

DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. & W11 \\

>>>>

Also for plotting convenience, for transiting $Kepler$ planets without
$m\sin{i}$ measured, we estimate their mass using mass-radius
relations from the literature. We follow a series of relations given
by \footnote{As of the writing of this manuscript, Kepler planet
  candidates on exoplanets.org ingested from the Exoplanet Archive
  have their masses estimated in a slightly different manner.  The
  Website uses the \citeauthor{Mordasini2012} relation for planets
  with 6$\rearth < R < b$ ($b \sim 11 \rearth$ as defined by
  \citeauthor{Mordasini2012}), the \citeauthor{Lissauer2011} relation
  between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in Earth
  units for planets smaller than $\rearth$.  Updating this relation to
  be consistent with the EOD (and updating the corresponding MASSREF
  fields for these candidates) is a priority upgrade for
  exoplanets.org.}

@@

%------------------------------------------------------------------------------
%\subsection{Uncertainties and Upper Limits}\label{sec:unc}
\subsection{Uncertainties}\label{sec:unc}

@@

\begin{comment}
If only an upper limit is given, we set the parameter field X to 0,
and store the upper limit value in the field XUL. The uncertainty UX
is set to half of the upper limit, and the upper error bar XUPPER to
the upper limit value. For example, if the literature reports the
upper limit for ECC, which we report in ECCUL, then we set ECC to be
0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We are currently
implementing a more precise upper limit scheme (see
Section~\ref{sec:summary}.)
\end{comment}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/senew.eps}
\caption{An example plot that demonstrates the current secondary
  eclipse measurements. Each planet has a set of circles that stand
  for its available secondary eclipse measurements in the database,
  including \spitzer\ 8.0, 5.8, 4.5, \& 3.6 \micron, and ground-based
  $J$, $H$, and $K_{\rm s}$ bands. \kepler\ secondary eclipse measurements
  are labeled as solid black dots. A few representative planets are
  also annotated (a feature not offered by the EDE Plotter, but
  trivially implemented by other image or presentation software). The
  planet name will appear when the user points the cursor at the
  corresonding data point in the interactive plotting tools.}
\label{fig:se}
\end{figure}

@@

DEPTH\dotfill & Float & Transit depth, or $(R_p/R_*)^2$ when depth is
not given & -UPPER, etc. & W11 \\
